Analyses

### 2021-11-10 src/analysis/analyses.Rmd
add data analyses
add data analysis

## Ethnic Conception Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
```

@@

>>>>

## Ethnic Conception Hypothesis 
```{r "h1", fig.align="center", fig.height=8, fig.width=8}
source(here("src/analysis/h1.R"))
p1
# negative values: Ethnic conception > Civic conception 
# positive values: Ethnic conception < Civic conception 
```

@@

```{r "h2", fig.align="center", fig.height=6, fig.width=10, echo = FALSE, fig.show = "hide"}
p2a + p2b + 
  plot_layout(widths = c(2, 1))
```
